Software Citation Principles

### 2016-07-30 sc-principles/software-citation-principles.tex
materialize -> materialized

The group gathered members (see Appendix~\ref{app:wg_members}) in April and
May 2015, and then began work in June. This materialize as a number of meetings
and offline work by group members to document existing
practices in member disciplines; gather materials from workshops and other
reports; review those materials, identifying overlaps and differences;
create a list of use cases related to software citation, recorded in
Appendix~\ref{app:usecases}; and subsequently draft an initial version of this document.
The draft Software Citation Principles document was discussed in a day-long
workshop and presented at the FORCE2016 Conference~\cite{force2016} in April 2016.
Members of the workshop and greater FORCE11 community gave feedback, which we
recorded here in Appendix~\ref{app:force16-feedback}. This discussion led to
some changes in the use cases and discussion, although the principles themselves
were not modified. We also plan to initiate a follow-on working group that will
work with stakeholders to ensure that these principles impact the research process.

>>>>

The group gathered members (see Appendix~\ref{app:wg_members}) in April and
May 2015, and then began work in June. This materialized as a number of meetings
and offline work by group members to document existing
practices in member disciplines; gather materials from workshops and other
reports; review those materials, identifying overlaps and differences;
create a list of use cases related to software citation, recorded in
Appendix~\ref{app:usecases}; and subsequently draft an initial version of this document.
The draft Software Citation Principles document was discussed in a day-long
workshop and presented at the FORCE2016 Conference~\cite{force2016} in April 2016.
Members of the workshop and greater FORCE11 community gave feedback, which we
recorded here in Appendix~\ref{app:force16-feedback}. This discussion led to
some changes in the use cases and discussion, although the principles themselves
were not modified. We also plan to initiate a follow-on working group that will
work with stakeholders to ensure that these principles impact the research process.
